Hydras \& Co.

### 2023-06-30 doc/chapter-fol.tex
minor corrections
more documentation

@@

\begin{todo}
Link to subAll.v
\end{todo}

\begin{todo}
Make a chapter!
\end{todo}
\section{Languages for Arithmetic}

@@

\subsection{Contexts as lists}
\begin{todo}
Describe the \texttt{Prf} type (from \texttt{folProof.v}).

Give examples in a toy language.

>>>>

\inputsnippets{FolExamples/substExample1}

@@

The function \texttt{subFormula} defined in
\href{../theories/html/hydras.Ackermann.subAll.html}{Ackermann.subAll} allows to substitute a term $t_i$ to ecah free occurrence of the variable $v_i$ in a formula $F$. The dependance of $t-i$ from $v_i$ is given through a function from \texttt{nat} to
(\texttt{Term L}).

\inputsnippets{FolExamples/subAllExample1}

\subsection{Proof trees}

Proof trees in first-order logic are the inhabitants of the \texttt{Prf $L$} 
inductive type, defined in \href{../theories/html/hydras.Ackermann.folProof.html}{Ackermann.folProof}. Since this type has 14 constructors, we present
them one by one, after quoting its full definition.

Please note that the following constructions are parametrized with an
arbitrary language $L$, decared in the \texttt{ProofH} section.

\inputsnippets{folProof/prelude}

\inputsnippets{folProof/PrfDef}

\subsubsection{\texttt{Prf}'s type}

We want to define a data type  \texttt{Prf $l$ $F$}  of ``proof trees of the formula $F$, where $l$ is the list of assumptions used in the proof, enumerated left-to-right (\emph{i.e.} the fringe of the proof tree)''. 
Please note that this representation

\inputsnippets{folProof/PrfAbout}

\subsubsection{The axiom rule}

Let $A$ be a formula on $L$.  The \texttt{AXM} rule builds a proof-tree
of $A$ which uses \emph{exactly} the singleton list \texttt{[$\,A\,$]}.

\inputsnippets{folProof/AXM}

\inputsnippets{FolExamples/PrfEx1}

\subsubsection{Modus Ponens}

\inputsnippets{folProof/MP}

\inputsnippets{FolExamples/PrfEx2}

\inputsnippets{FolExamples/eat}

\begin{todo}
Give examples in a toy language.

\section{Languages for Arithmetic}

\begin{todo}
Make a chapter!
\end{todo}

@@
